Supporting Information

### 2018-02-27 SupportingInformation.Rmd
added functionality to the non-parametric test of tail dependence and asymmetry of tail dependence for soil C and N data

@@

<!--DAN: wherever copsync is needs to be sourced and also added to the mlist below-->
```{r stat_soilCN, echo=F, cache=T, cache.extra=list(seed,v,mlist(list("CopulaFunctions.R","copsurrog2d.R")))}
set.seed(seed) 
resloc<-"./Results/stat_results/stat_soilCN/"

#get the stats for the real data
stat_soilCN<-copsync(v) 
saveRDS(stat_soilCN,paste(resloc,file="stat_soilCN.RDS",sep=''))
sCN<-stat_soilCN[c(2:5,7,8,10:13)]
stat<-unlist(sCN)

#get surrogates and get stats for them
cop<-normalCopula(.5,2)
surv<-copsurrog2d(v,cop,1000)
#DAN: once you get the code for copsync, apply it to each surrogate and keep the results
```

<!--DAN: modify the table so it also shows tail asymmetry stats (differences) and also shows fractions of surrogates for both the tail dependence stats and the asymmetry stats that are greater than the real data stat-->
```{r table_stat_soilCN, echo=F, results="asis"}
table_nums("table_stat_soilCN",display=F)

knitr::kable(data.frame(stat=stat),caption = "Non-parametric stats on soil C/N dataset")
```

<!--DAN: The below will no longer be necessary once you make the above changes-->
```{r ,echo=F}
#sCN
CorlmCoru<-stat_soilCN$Corl-stat_soilCN$Coru
cat("Corl-Coru = ",CorlmCoru,"\n")
PlmPu<-stat_soilCN$Pl-stat_soilCN$Pu
cat("Pl-Pu = ",PlmPu,"\n")
TlmTu<-stat_soilCN$Tl-stat_soilCN$Tu
cat("Tl-Tu = ",TlmTu,"\n")
D2umD2l<-stat_soilCN$D2u-stat_soilCN$D2l
cat("D2u-D2l = ",D2umD2l,"\n")
```

>>>>

<!--Shya pls add a description of each of the statistics implemented in CopulaFunctions.R. As usual, please describe the stats with sufficient precision that they could be re-coded by the reader.-->

@@

### Non-paramtric analysis of tail dependence
<!--Do the analysis-->
```{r stat_soilCN, echo=F, cache=T, cache.extra=list(seed,v,mlist(list("CopulaFunctions.R","copsurrog2d.R","NonParamStat.R")))}
set.seed(seed) 
resloc<-"./Results/stat_results/stat_soilCN/"

#get the stats for the real data
stat_soilCN<-copsync(v) 
saveRDS(stat_soilCN,paste(resloc,file="stat_soilCN.RDS",sep=''))
sCN<-stat_soilCN[c(2:5,7,8,10:13)]
stat<-unlist(sCN)
stat<-c(stat[1:4],unname(stat[3]-stat[4]),stat[5:6],unname(stat[5]-stat[6]),stat[7:8],unname(stat[7]-stat[8]),stat[9:10],unname(stat[9]-stat[10]))
names(stat)[c(5,8,11,14)]<-c("Corl_m_Coru","Pl_m_Pu","Tl_m_Tu","D2l_m_D2u")

#get surrogates and get stats for them
cop<-normalCopula(.5,2)
numsurrog<-1000
surv<-copsurrog2d(v,cop,numsurrog)
statsurr<-matrix(NA,length(stat),numsurrog)
rownames(statsurr)<-names(stat)
for (counter in 1:dim(surv)[3])
{
  h<-copsync(surv[,,counter])
  h<-unlist(h[c(2:5,7,8,10:13)])
  h<-c(h[1:4],h[3]-h[4],h[5:6],h[5]-h[6],h[7:8],h[7]-h[8],h[9:10],h[9]-h[10])
  statsurr[,counter]<-unname(h)
}

#now get fractions of surrogates lt the data and gt the data for each stat
stattab<-data.frame(statname=names(stat),stat=unname(stat),frac_surr_gt=NA,frac_surr_lt=NA)
for (counter in 1:length(stat))
{
  stattab[counter,3]<-sum(statsurr[counter,]>stat[counter])/numsurrog
  stattab[counter,4]<-sum(statsurr[counter,]<stat[counter])/numsurrog
}
```

<!--Display the table generated above-->
```{r table_stat_soilCN, echo=F, results="asis"}
table_nums("table_stat_soilCN",display=F)
knitr::kable(data.frame(stat=stattab),caption = "Results of non-parametric tests of tail dependence and asymmetry of tail dependence for the soil C and N dataset.")
```
